A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2019-01-09 doc/large_strain.tex
mention that we won't study GMG in details (not the focus)

{\color{red}
To summarize, in this section we propose a method by which to construct level tangent operators for finite-strain elasticity to be employed within the GMG preconditioner.
The other parts of the GMG preconditioner such as Chebyshev smoother, matrix-free interlevel transfer operators and the coarse level iterative solver are provided by the \texttt{deal.II} library.
We note that at the time of writing, $p-$ version of the GMG is not available within the \texttt{deal.II} library.
}

>>>>

{\color{red}
To summarize, in this section we propose a method by which to construct level tangent operators for finite-strain elasticity to be employed within the GMG preconditioner.
The other parts of the GMG preconditioner such as Chebyshev smoother, matrix-free interlevel transfer operators and the coarse level iterative solver are provided by the \texttt{deal.II} library.
The efficiency of the preconditioner, from the perspective of linear algebra, with the so defined level operators will be assessed by numerical examples in the next section.
We will, however, refrain from studying the machine performance aspects of the multigrid preconditioner as a whole as the focus of this paper is the matrix-free implementation of tangent operators of finite-strain elasticity both at the fine mesh level as well as the coarser multigrid levels.
Finally, we note that at the time of writing, $p-$ version of the GMG is not available within the \texttt{deal.II} library.
}
